Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-06-13 manuscript/manuscript.tex
propositions in manuscript

\usepackage{natbib}

@@

\newcommand{\jy}[1]{\textcolor{blue}{JY: (#1)}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

@@

The standard one-sample Kolmogorov--Smirnov (KS) test is widely
recognized as an effective good-of-fit test for continuous distributions.
Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
hypothesized distribution~$F(x; \theta_0)$, where $\theta_0$ are the 
specified parameters
of the hypothesized distribution family.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
\end{equation}
As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. This distribution function is
precisely computable using contemporary statistical software
\citep{marsaglia2003evaluating}. The versatility of the KS test allows its
application across various domains, such as analyzing cosmic microwave
background radiation \citep{naess2012application}, monitoring the count rate of
radioactive data \citep{aslam2020introducing}, gear condition monitoring
\citep{andrade2001gear}, studying images of breast cancer tumors
\citep{demidenko2004kolmogorov}, and examining financial markets
\citep{lux2001turbulence}.

@@

Developing a fully nonparametric solution for the KS 
tests in the presence of serially dependent data presents a significant 
challenge. The null distribution's characteristics are intricately linked to 
the structure of the serial dependence, which can vary widely in practical 
situations. Employing a nonparametric method would necessitate defining a 
specific model for this dependence, despite the primary focus being on 
evaluating the marginal distribution of a stationary series. To date, a bias 
correction method for block bootstrap, akin to the NPB
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks 
to bridge this gap by introducing a bias correction technique for the 
nonparametric block bootstrap (NPBB), tailored for use in scenarios where the 
hypothesized distribution has unspecified parameters and the data 
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent. 
As noted by 
\citet{chandy2024sample}, a sample greater than 1600 may be necessary for 
block bootstrap confidence intervals to have the right coverage 
rates of parameters. 
Therefore, although this study uses block bootstrap in a different setting,
we expect that a large sample size may be required when the data is serially
dependent.

The remainder of this paper is structured as follows: 
Section~\ref{sec:methods} provides an overview of the block bootstrap 
procedure and introduces the bias correction methodology for the 
NPBB KS test. Section~\ref{sec:simu} is divided 
into two parts; initially, we evaluate the KS test's ability to maintain 
its size, i.e., its consistency in not rejecting the null hypothesis when 
it is indeed true. Subsequently, we examine the test's power, assessing 
whether it can reject the null hypothesis when it is false. Practical 
applications of our method are presented in Section~\ref{sec:real}, where 
we apply the approach to analyze if S\&P 500 index stock return
data adheres to either the Normal or the Student's $t$ distribution. The 
paper concludes with Section~\ref{sec:conclusion}, offering final thoughts
and remarks.

@@

First, let us review how the KS statistic is computed for an independent
sample with fitted parameters. Let $\hat\theta_n$ denote the parametrically
fitted parameters, which can be obtained from any consistent estimator with
asymptotic normality properties.  Let $F_n$ be the empirical distribution
function based on $X_1,...,X_n$.
Define 
\begin{equation*}
Y_n(x; \hat\theta_n) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the one-sample KS goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta_n)|.
\end{equation*}

Because of the estimation uncertainty in $\hat\theta_n$, the asymptotic
distribution of $Y_n$ is no longer distribution-free. This is in contrast to the
case where $\theta$ is known.  Note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x)).
\end{equation*}
When $\hat\theta_n$ is replaced with $\theta$, as in the standard KS testing
situation, the second term vanishes, and $T_n$ converges in distribution to that
of $\sup_t | B(F(t)) |$, where $B(\cdot)$ is the standard Brownian bridge
\citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the
second term leads to a bias in the Brownian bridge, which was addressed by
\citet{babu2004goodness}.

\eds{Please check consistency with how you refer to $F$.  In 
Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
parameter arguments are separated by a semicolon.  At the beginning of 
Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
separating the data argument from the parameter argument (and no 0 subscript
either).   Then in this first 
subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
arguments.  Then immediately above its use is mixed with $F(x)$ without a 
parameter argument (implying it is the true parameter $\theta$). This continues
throughout the document. I suggest either using consistent notation throughout, 
or explicitly defining any shortened/simplified notation at its first use.}
\mc{switched everything to semicolons}

@@

\subsection{Nonparametric bootstrap (NPB) for independent data}

Continue with the case where $X_i$'s are independent but the parameters
are unspecified. Denote by
$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
$\sqrt{n}(F_n(x) - F(x))$ and $\sqrt{n}(F(x; \hat\theta_n) - F(x))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected to approximate the distribution of $T_n$. We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

In summary, the procedure of the NPB KS test for independent
sample is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying basic bootstrap 
  on the original sample as
  defined previously.
\item
  Obtain parametrically
  fitted parameters 
	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
	\eds{$F_\theta$ has not yet been defined.}\mc{addressed}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
  bias term.
\end{enumerate}

@@

\subsection{Nonparametric block bootstrap (NPBB) for stationary series}

@@

Then, we can define
\begin{align*}
  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)]) - 
             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n)]) \\
           &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
             \sqrt{n}(E[F^{(b)}_n(x)] - F(x; E[\hat\theta^{(b)}_n])),
\end{align*}
and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$. Each $T_n^{(b)}$,
$b =1, \ldots, B$, is considered a draw from a distribution that approximates
the distribution of $T_n$. Therefore, the p-value of the observed statistic
$T_n$ can be assessed by positioning it agains the empirical distribution of
$T_n^{(b)}$, $b = 1, \ldots, B$.

\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}

In summary, the procedure of the NPBB test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

The p-value of the block bootstrap KS test can be approximated
as $p = \sum_{b=1}^N I\{T^{(b)}_n > T_n\} / B$.

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot ; \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot ; \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
\mc{changed everything to semicolon}
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 1000\}$
for the test when applied to samples from the same data generating process.
\eds{I assume $r$ is for replicate?  Please define and include how many 
total replicates you are using.} \mc{addressed}

@@

Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
plots of the p-values testing the marginal distribution of the stationary time
series generated from the null hypothesis, created with R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line. The plots suggest that the extent to which the p-values are
uniformly distributed is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be uniformly
\eds{uniformly?}\mc{addressed} distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

\begin{table}[tbp]
\centering
\caption{Rejection rates or true size for test that sample follows its true
                    distribution family for
                   different values of AR(1) coefficient and for different 
                   significance levels or estimated sizes.
		\eds{Not sure if it will help presentation or interpretation, but you could
	consider presenting the values inside the table as estimated size/true size}
	\mc{addressed}}
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 0.052 & 0.013& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
& {200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
& {400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
& {800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\
  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
  & {200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
  & {400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
  & {800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

\usepackage{natbib}
\usepackage{lipsum}

@@

\newcommand{\jy}[1]{}
\newcommand{\eds}[1]{}
\newcommand{\mc}[1]{}

@@

The standard one-sample Kolmogorov--Smirnov (KS) test is widely
recognized as an effective good-of-fit test for continuous distributions.
Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
hypothesized distribution~$F(x; \theta_0)$, where $\theta_0$ are the 
specified parameters
of the hypothesized distribution family.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\[
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
\]
As sample size $n\to \infty$, the distribution of $T_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. This distribution function is
precisely computable using contemporary statistical software
\citep{marsaglia2003evaluating}. The versatility of the KS test allows its
application across various domains, such as analyzing cosmic microwave
background radiation \citep{naess2012application}, monitoring the count rate of
radioactive data \citep{aslam2020introducing}, gear condition monitoring
\citep{andrade2001gear}, studying images of breast cancer tumors
\citep{demidenko2004kolmogorov}, and examining financial markets
\citep{lux2001turbulence}.

@@

Developing a fully nonparametric solution for the KS 
tests in the presence of serially dependent data presents a significant 
challenge. The null distribution's characteristics are intricately linked to 
the structure of the serial dependence, which can vary widely in practical 
situations. Employing a nonparametric method would necessitate defining a 
specific model for this dependence, despite the primary focus being on 
evaluating the marginal distribution of a stationary series. To date, a bias 
correction method for block bootstrap, akin to the NPB
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks 
to bridge this gap by introducing a bias correction technique for the 
nonparametric block bootstrap (NPBB), tailored for use in scenarios where the 
hypothesized distribution has unspecified parameters and the data 
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent.

The remainder of this paper is structured as follows: 
Section~\ref{sec:methods} provides an overview of the block bootstrap 
procedure and introduces the bias correction methodology for the 
NPBB KS test. Section~\ref{sec:simu} is divided 
into two parts; initially, we evaluate the NPBB KS test's ability to maintain 
its size, i.e., its consistency in not rejecting the null hypothesis when 
it is indeed true. Subsequently, we examine the NPBB KS test's power, assessing 
whether it can reject the null hypothesis when it is false. Practical 
applications of our method are presented in Section~\ref{sec:real}, where 
we apply the approach to analyze if S\&P 500 index stock return
data adheres to either the Normal or the Student's $t$ distribution. The 
paper concludes with Section~\ref{sec:conclusion}, offering final thoughts
and remarks.

@@

First, let us review how the KS statistic is computed for an independent
sample with fitted parameters. Let $\hat\theta_n$ denote the parametrically
fitted parameters, which can be obtained from any consistent estimator with
asymptotic normality property.  Let $F_n$ be the empirical distribution
function based on $X_1,...,X_n$.
Define 
\begin{equation*}
Y_n(x; \hat\theta_n) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the one-sample KS goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta_n)|.
\end{equation*}

Because of the estimation uncertainty in $\hat\theta_n$, the asymptotic
distribution of $Y_n$ is no longer distribution-free. This is in contrast to the
case where $\theta$ is known.  Note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \theta_0)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0)),
\end{equation*}
where $\theta_0$ is the true parameter value of $\theta$ under~$H_0$.
When $\hat\theta_n$ is replaced with $\theta_0$, as in the standard KS testing
situation, the second term vanishes, and $T_n$ converges in distribution to that
of $\sup_t | B(F(t; \theta_0)) |$, where $B(\cdot)$ is the standard Brownian bridge
\citep{kolmogorov1933sulla}. With $\hat\theta_n$ in place of $\theta$, the
second term leads to a bias in the Brownian bridge, which was addressed by
\citet{babu2004goodness}.

%\eds{Please check consistency with how you refer to $F$.  In 
%Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
%parameter arguments are separated by a semicolon.  At the beginning of 
%Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
%separating the data argument from the parameter argument (and no 0 subscript
%either).   Then in this first 
%subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
%arguments.  Then immediately above its use is mixed with $F(x)$ without a 
%parameter argument (implying it is the true parameter $\theta$). This continues
%throughout the document. I suggest either using consistent notation throughout, 
%or explicitly defining any shortened/simplified notation at its first use.}
%\mc{switched everything to semicolons}
%\jy{replaced $F$ with $F(\cdot; \theta_0)$}

@@

\subsection{NPB for independent data}

Continue with the case where $X_i$'s are independent but the parameters
are unspecified. Denote by
$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$ and
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected to approximate the distribution of $T_n$. We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

In summary, the procedure of the NPB KS test for an independent sample is
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by sampling $X_1, \ldots, X_n$
  with replacement.
\item
  Obtain parametrically
  fitted parameters 
	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
	%\eds{$F_\theta$ has not yet been defined.}\mc{addressed}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
  bias term.
\end{enumerate}

@@

\subsection{NPBB for stationary series}
\label{sub:npbb}

@@

Then, we can define
\begin{align*}
  Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)]) - 
             \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n)]) \\
           &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) -
             \sqrt{n}(E[F^{(b)}_n(x)] - F(x; E[\hat\theta^{(b)}_n])),
\end{align*}
and $T^{(b)}_n = \sup_x|Y^{(b)}_n(x)|$. Each $T_n^{(b)}$,
$b =1, \ldots, B$, is considered a draw from a distribution that approximates
the distribution of $T_n$. Therefore, the p-value of the observed statistic
$T_n$ can be assessed by positioning it against the empirical distribution of
$T_n^{(b)}$, $b = 1, \ldots, B$.

%\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
%  the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}

We will assume that the time series $\{X_t\}$ is stationary and strongly mixing, 
and $1/l+l/n\rightarrow 0$. We aim to show that under suitable assumptions
\begin{enumerate}
    \item $T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|$ 
    for some Gaussian process $G_{\infty}(\cdot)$ and Gaussian random variable 
    $U$ defined below.
    \item $|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$ for any fixed $x,$ 
    where $X_{1:n}:=\{X_1,\dots,X_n\}$ and $T_n^*$ is the the statistic computed 
    based on the bootstrap sample $X_1^*,\dots,X_n^*$). 
    Following the arguments in the proof of the Glivenko-Cantelli Theorem, we 
    may further strengthen this result to allow uniform convergence over $x$: 
    in other words, $\sup_x|\mathbb{P}(T_n^*\leq x|X_{1:n}) - 
    \mathbb{P}(T_n\leq x)|\overset{a.s.}{\rightarrow} 0$.
\end{enumerate}
Sketches of the proofs for these propositions are shown as supporting 
information.

In summary, the procedure of the NPBB test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  %Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	%$\hat\theta^{(b)}_n$ of $\theta$.
	Obtain parametrically fitted parameters 
	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
	\eds{changed this to remove $F_\theta$, please check}\mc{looks good}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x \Big\vert \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) \Big\vert.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

The p-value of the block bootstrap KS test can be approximated
as $p = \sum_{b=1}^B I\{T^{(b)}_n > T_n\} / B$.

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot ; \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot ; \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
%\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
%\mc{changed everything to semicolon}
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times 
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating process.
%\eds{I assume $r$ is for replicate?  Please define and include how many 
%total replicates you are using.} \mc{addressed}

@@

Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
plots of the p-values testing the marginal distribution of the stationary time
series generated from the null hypothesis, created with R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line. The plots suggest that the extent to which the p-values are
uniformly distributed is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be uniformly distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

\begin{table}[tbp]
\centering
\caption{Empirical sizes (ratio of rejection rate to significance level)
for the test that sample follows its true
                    distribution family for
                   different values of AR(1) coefficient and for different 
                   significance levels.
		\eds{Not sure if it will help presentation or interpretation, but you could
	consider presenting the values inside the table as estimated size/true size}
	\mc{addressed}
	\eds{I meant reporting the ratio, e.g, dividing all values currently in the    first row by 0.01, dividing all values in the second row by 0.05. Sometimes this
	is helpful if there is a conservative or liberal pattern, which there seems
	to be as $|\tau|$ increases away from zero, but it may be fine to leave it as
	is.}\mc{how does this look?}}
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 5.210 & 1.240 & 1.120 & 1.060 & 1.140 & 1.580 & 5.630 \\ 
& & 0.05 & 2.940 & 1.256 & 1.090 & 1.096 & 1.150 & 1.450 & 3.410 \\ 
& & 0.10 & 2.277 & 1.186 & 1.147 & 1.072 & 1.154 & 1.424 & 2.714 \\ 
& {200} & 0.01 & 4.390 & 1.130 & 0.900 & 1.140 & 1.090 & 1.380 & 5.900 \\ 
& & 0.05 & 2.556 & 1.120 & 1.020 & 1.064 & 1.092 & 1.382 & 3.452 \\ 
& & 0.10 & 2.080 & 1.123 & 1.069 & 1.086 & 1.051 & 1.332 & 2.650 \\ 
& {400} & 0.01 & 3.240 & 1.070 & 0.990 & 1.080 & 0.970 & 1.260 & 4.670 \\ 
& & 0.05 & 2.032 & 1.000 & 0.994 & 1.120 & 0.978 & 1.184 & 2.836 \\ 
& & 0.10 & 1.734 & 1.023 & 1.002 & 1.089 & 1.017 & 1.192 & 2.232 \\ 
& {800} & 0.01 & 2.520 & 0.900 & 0.980 & 1.110 & 1.020 & 1.350 & 3.540 \\ 
& & 0.05 & 1.766 & 1.008 & 0.972 & 0.956 & 0.962 & 1.236 & 2.438 \\ 
& & 0.10 & 1.555 & 1.026 & 0.986 & 0.961 & 0.997 & 1.206 & 2.044 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 4.880 & 1.420 & 1.170 & 1.240 & 1.110 & 1.610 & 5.760 \\ 
  & & 0.05 & 2.850 & 1.282 & 1.222 & 1.170 & 1.178 & 1.464 & 3.374 \\ 
  & & 0.10 & 2.241 & 1.224 & 1.147 & 1.175 & 1.150 & 1.375 & 2.679 \\ 
  & {200} & 0.01 & 4.080 & 1.000 & 0.890 & 1.220 & 1.160 & 1.430 & 6.080 \\ 
  & & 0.05 & 2.510 & 1.118 & 1.014 & 1.068 & 1.116 & 1.290 & 3.380 \\ 
  & & 0.10 & 1.991 & 1.105 & 1.022 & 1.048 & 1.072 & 1.233 & 2.664 \\ 
  & {400} & 0.01 & 3.140 & 0.970 & 1.140 & 0.940 & 1.030 & 1.310 & 4.300 \\ 
  & & 0.05 & 2.004 & 0.964 & 1.042 & 1.062 & 1.122 & 1.236 & 2.808 \\ 
  & & 0.10 & 1.697 & 1.025 & 1.066 & 1.018 & 1.100 & 1.177 & 2.232 \\ 
  & {800} & 0.01 & 2.490 & 0.920 & 1.130 & 1.120 & 1.000 & 1.130 & 3.810 \\ 
  & & 0.05 & 1.804 & 0.976 & 1.064 & 1.022 & 1.086 & 1.196 & 2.474 \\ 
  & & 0.10 & 1.561 & 1.024 & 1.072 & 1.034 & 1.067 & 1.177 & 1.997 \\ 
   \bottomrule
\end{tabular}
\end{table}
